---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# brandseyer2 

  <!-- badges: start -->
  [![R build status](https://github.com/brandseye/brandseyer2/workflows/R-CMD-check/badge.svg)](https://github.com/brandseye/brandseyer2/actions)
  <!-- badges: end -->

brandseyer2 is a library for handling data in your BrandsEye account.

[BrandsEye][brandseye] is an opinion mining company. We use a proprietary mix of artificial intelligence
and crowdsourcing to mine online conversations for sentiment.
While we have an analytics suite, and reporting service, we also provide an extensive API
to access to the data that makes up your various BrandsEye accounts, and makes it easy to
access the data outside of the BrandsEye application in any [R][R] analyses that you might want to
perform.

This version of the library is still in its early stages, but is usable,
and is the preferred way of getting data from the API. You should probably be using
this over the previous version of the API, available at [GitHub][brandseyer].

The goal of this version of the library is:

- to fully support our new API, 
- to better support the [tidyverse][tidyverse] set of libraries,
- and to have a test suite.

There may be breaking changes to some methods in future updates, before the version 1.0.0 release,
After that, we expect that the API should be fairly stable. 

# Getting started

After installing, you may find the [Getting Started](https://brandseye.github.io/brandseyer2/articles/brandseyer2.html) 
and [Cookbook](https://brandseye.github.io/brandseyer2/articles/cookbook.html) vignettes interesting
to read or skim through. 

# Installing

You can install the development version of this library using the `devtools` package:

```{r eval=FALSE}
# Install the devtools package
install.packages("devtools")
library(devtools)

# Install the library
install_github("brandseye/brandseyer2")

# Load the library
library(brandseyer2)
```

When using the development version from github, you should make sure that the build
is passing before installing it. Check the build badge on the library's github page.

# Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.

# License

This library is licensed under the MIT license, and is copyright Brandseye PTY (LTD). See
the license files for details.


[brandseyer]: https://github.com/brandseye/brandseyer  "The original brandseyer library"
[R]: http://www.r-project.org/
[brandseye]: http://www.brandseye.com
[tidyverse]: https://www.tidyverse.org/
