---
title: "brandseyer2"
author: "Constance Neeser"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{brandseyer2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(brandseyer2)

```

# Who is BrandsEye and what is brandseyer2?

# Authenticating yourself

brandseyer2 provides API access to the BrandsEye API. In order to identify who you 
are, we provide our users with API keys on request. API keys are strings of randomly
generated characters and numbers — they are difficult to guess, and very secure. 

You can contact your account manager to get your API key. Once you have your API key,
the first step to using brandseyer2 is to authenticate yourself, which you can
do as follows:

```{r eval=FALSE}
library(brandseyer2)
authenticate(key = "<my api key>")
```

This will let brandseyer2 know who you are. If you don't want to type this in
every time that you use brandseyer2, you can tell brandseyer2 to save your api
key.

```{r eval=FALSE}
authenticate(key = "<my api key>", save = TRUE)
```

Now, every time the library is loaded, brandseyer2 will immediately start using
the saved API key.

Along with the `authenticate` function, you can also find out whose API key
brandseyer2 is using:

```{r eval=FALSE}
whoami()
#> login:  Constance Neeser 
#> email:  noreply@brandseye.com
```

Now that you have authenticated yourself, you can begin to access your
account information and mentions.

## Protecting your API key

- Don't share with others
- Don't submit them to source code repositories.

## What to do if things go bad?

Contact your account manager. They'll provide you with a new API key.
Your previous API key will stop working. 

# Working with accounts

What is an account?

## What accounts do I have access to?

## Brands

## Tags

## Topics


