---
title: "brandseyer2"
author: "Constance Neeser"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{brandseyer2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(brandseyer2)

```

# Who is BrandsEye and what is brandseyer2?

BrandsEye: opinion mining. Sentiment and topics. 

What is sentiment? It's always towards somethings. And people 
may be talking about particular topics. 

## Data sources

## The BrandsEye Crowd

# Authenticating yourself

brandseyer2 provides API access to the BrandsEye API. In order to identify who you 
are, we provide our users with API keys on request. API keys are strings of randomly
generated characters and numbers — they are difficult to guess, and very secure. 

You can contact your account manager to get your API key. Once you have your API key,
the first step to using brandseyer2 is to authenticate yourself, which you can
do as follows:

```{r eval=FALSE}
library(brandseyer2)
authenticate(key = "<my api key>")
```

This will let brandseyer2 know who you are. If you don't want to type this in
every time that you use brandseyer2, you can tell brandseyer2 to save your api
key.

```{r eval=FALSE}
authenticate(key = "<my api key>", save = TRUE)
```

Now, every time the library is loaded, brandseyer2 will immediately start using
the saved API key.

Along with the `authenticate` function, you can also find out whose API key
brandseyer2 is using:

```{r eval=FALSE}
whoami()
#> BrandsEye Credentials
#>   name:  Constance Neeser
#>   email: connie@brandseye.com 
```

Now that you have authenticated yourself, you can begin to access your
account information and mentions.

## Protecting your API key

- Don't share with others
- Don't submit them to source code repositories.

## What to do if things go bad?

Contact your account manager. They'll provide you with a new API key.
Your previous API key will stop working. 

# Overview

What is an account? What are mentions? What is the crowd, and sentiment and topics. 

Some simple examples of pulling mentions for accounts, grouping, updating.

An account collects and structures the data that BrandsEye collects and processes for you.
The smallest bit of data that we collect is a _mention_. A _mention_ is a post
on some social media network — for example, a tweet, or a facebook post, is a _mention_. 

We collect mentions in _brands_. Brands define the point of interest of the mentions. 
Example brands may be the name of your company, a competitor, a well known individual,
and so on. The sentiment of a mention is always measured towards the brand that the 
mention is collected in, and the brands also define what the _topics_ that a mention
may be about are. 

Brands also organise the search _phrases_ that we use to find mentions online for you.

Brands themselves are collected in _accounts_. Accounts also store extra information,
such as what people get to access the data, how much Crowd verification the data receives,
and so on.

# Working with accounts

As someone who works with BrandsEye tools, you have a collection of accounts
that you have access to. You can find this collection of accounts using
`account_list()`, as follows:

```{r, eval=FALSE}
account_list()
```

This returns a tibble of accounts that are available to you. Importantly, 
it lets you find the account code (listed in the `account`, such as `TEST01AA` and `TEST02AA`) 
column that brandseyer2
uses to reference individual accounts.


## Referencing an account

Nearly all the functions in brandseyer2 needs an account reference. You can refer to any account
using it's account code and the `account()` function. For example:

```{r}
# Get a reference to the account TEST01AA
account("TEST01AA")
```

Many operations that you may want to perform will begin with finding an account
reference, and then passing this on to other brandseyer2 functions using the pipe operator, `%>%`.

Here are some examples to find the name, code, and account manager of your account:

```{r}
# Your account's name
account("TEST01AA") %>% 
  account_name()
```

```{r}
# Your account code
account("TEST01AA") %>% 
  account_code()
```

```{r}
# Your account manager.
account("TEST01AA") %>% 
  account_manager()
```


## Brands

Accounts are made up of _brands_. It is brands themselves that store individual _mentions_
(such as tweets, facebook posts, and so on). 

A brand is usually something that you would like to 
track on social media, and measure sentiment towards. All sentiment on a mention is always
towards the brand that the mention belongs to.

You can find out what brands are in your account using the `brands()` function. Let's have
a look at what brands are in _TEST01AA_:

```{r}
account("TEST01AA") %>% 
  brands()
```

These tibbles can become a bit tight to display all of the data that you may want to see. 
If you are using RStudio, you can always pipe the results in to View(). Otherwise, you can 
subselect for the data you want using standard dplyr[^1] functions.

```{r message=FALSE, warning=FALSE}
# Find brand IDs and names
library(dplyr)

account("TEST01AA") %>% 
  brands() %>% 
  select(id, name, parent)
```

There, that's better. Now you can see that your _TEST01AA_ account is made out of three
brands. We've also selected another column called `parent`. We've done this to show the
hierarchical nature of brands: some brands are children of other brands. Setting up an
account in this way can help you to organise the mentions that are collected in a brand
around more specific themes. 

You can also discover this information for all the accounts that you have
access to. 

```{r}
# Example here
```

Notice that one of our accounts have old brands that are no longer being used,
and have been deleted. Also, we often want to find the top level brands that
make up the main collections of mentions in an account. These "top level" brands
are called _root brands_. We have a convenient function that finds the root brands
currently in use in your account:

```{r}
account("TEST01AA") %>% 
  root_brands()
```


## Topics

## Tags

# Working with mentions

Mentions can be read using the `mentions()` function:


```{r}
account("TEST01AA") %>% 
  mentions(filter = "published inthelast week")
```

# Counting mentions

Mentions can be counted. The simplest way of doing this is
with the `count_mentions()` function, and using a query language
designed to do this.

Here is a simple query to count all mentions published the last week:

```{r, eval = FALSE}
account("QUIR01BA") %>% 
  filter_mentions("published inthelast week") %>% 
  count_mentions()
#> # A tibble: 1 x 1
#>   mentionCount
#>          <int>
#> 1         8907
```

More interestingly, we can count just the relevant mentions from the
last week:

```{r, eval = FALSE}
account("QUIR01BA") %>% 
  filter_mentions("published inthelast week and relevancy isnt irrelevant") %>% 
  count_mentions()
#> # A tibble: 1 x 1
#>   mentionCount
#>          <int>
#> 1         7918
```

If you would like to know more about filtering in particular, see our 
[Filtering](filtering.html) vignette.

Now, counting mentions becomes interesting when we begin to do things such as
grouping mentions. For example, we can group mentions by the published date.

```{r, eval = FALSE}
account("QUIR01BA") %>% 
  filter_mentions("published inthelast week and relevancy isnt irrelevant") %>% 
  group_mentions_by(published) %>% 
  count_mentions()
#> # A tibble: 8 x 2
#>   published           mentionCount
#>   <dttm>                     <int>
#> 1 2018-07-26 00:00:00         1410
#> 2 2018-07-27 00:00:00         1067
#> 3 2018-07-28 00:00:00          528
#> 4 2018-07-29 00:00:00          655
#> 5 2018-07-30 00:00:00         1389
#> 6 2018-07-31 00:00:00         1214
#> 7 2018-08-01 00:00:00         1124
#> 8 2018-08-02 00:00:00          532
```

This is something that you could potentially chart, using
a library such as [ggplot2](http://ggplot2.org/).

```{r echo=FALSE, fig.cap="A plot of data pulled from the api", message=FALSE, warning=FALSE, fig.width=5}
library(lubridate)
library(ggplot2)

data <- tibble::tribble(
  ~published,           ~mentionCount,
  ymd(20180726),         1410,
  ymd(20180727),         1067,
  ymd(20180728),          528,
  ymd(20180729),          655,
  ymd(20180730),         1389,
  ymd(20180731),         1214,
  ymd(20180801),         1124,
  ymd(20180802),          532
)

ggplot(data, aes(x = published, y = mentionCount)) +
  geom_bar(stat = "identity") +
  labs(x = "Published date", y = "Mention volume")

```

One thing to take note of is that at no point have we specified
what brands we want to use in the filter. This happens automatically:
the query language selects all the root brands. You can easily examine
this by leaving out the final step in the pipe chain above, like so:

```{r, eval = FALSE}
account("QUIR01BA") %>% 
  filter_mentions("published inthelast week and relevancy isnt irrelevant") %>% 
  group_mentions_by(published)
#> BrandsEye Query
#>   accounts:  QUIR01BA
#>   brands:    35 brands selected
#>   timezones: Africa/Johannesburg
#>   filter:    published inthelast week and relevancy isnt irrelevant
#>   grouping:  published
```

If you would like to see the filter being produced, you can do so using the
`to_count_filter()` method. Let's do this using an account with fewer root brands:

```{r}
# Let's see what the query looks like
account("TEST01AA") %>% 
  filter_mentions("published inthelast week and relevancy isnt irrelevant") %>% 
  group_mentions_by(published)

# And this is the filter
account("TEST01AA") %>% 
  filter_mentions("published inthelast week and relevancy isnt irrelevant") %>% 
  group_mentions_by(published) %>% 
  to_count_filter("TEST01AA")
```

Notice that the _group by_ doesn't occur in the filter: this is additional data
sent to the API when we request the data. This full filter is, however, sent to 
the API. It's also an appropriate filter for use in Analyse or anywhere else
that a filter is accepted.

A useful thing that the filter allows us to do is to count data across multiple
accounts at a time. For example, you across two specific brands:

```{r, eval = FALSE}
account("QUIR01BA", "BEUB03AA") %>% 
  filter_mentions("published inthelast week and relevancy isnt irrelevant") %>% 
  count_mentions()
#> # A tibble: 2 x 2
#>   account  mentionCount
#>   <chr>           <int>
#> 1 QUIR01BA         7951
#> 2 BEUB03AA         8466
```

Again, you can group by any grouping field that you would want. 

You can also count across all accounts that are available to you:

```{r, eval = FALSE}
account_list() %>% 
  account() %>% 
  filter_mentions("published inthelast week and relevancy isnt irrelevant") %>% 
  count_mentions()
#> # A tibble: 4 x 2
#>   account  mentionCount
#>   <chr>           <int>
#> 1 QUIR01BA         7951
#> 2 BEUB03AA         8466
#> 3 TEST01AA         1234
#> 4 TEST02AA         1234
```

A very useful thing that the query language provides us, is the ability to
compare sub-groups of mentions using sub-filters. For example, if we want
to find mentions inside and outside of Africa, we could so as follows:

```{r, eval = FALSE}
account("QUIR01BA", "BEUB03AA") %>% 
  filter_mentions("published inthelast week and relevancy isnt irrelevant") %>% 
  compare_mentions(africa = "location is 'africa'", elsewhere = "location isnt 'africa'") %>% 
  count_mentions()
#> # A tibble: 4 x 3
#>   account  comparison mentionCount
#>   <chr>    <chr>             <int>
#> 1 QUIR01BA africa              184
#> 2 QUIR01BA elsewhere          7139
#> 3 BEUB03AA africa             7850
#> 4 BEUB03AA elsewhere           295
```

We have provided two seperate sub-filters, one labeled 'africa', one labeled 'elsewhere'. 
Notice that these labels have now appeared in the result table, once for each account
that we are querying.


[^1]: [dplyr](https://dplyr.tidyverse.org/) is a great library for working with and manipulating your data sets. brandseyer2 is built around some patterns that you will find in dplyr itself.
