---
title: "The brandseyer2 Cookbook"
author: "Constance Neeser"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The brandseyer2 Cookbook}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This is a collection of short scripts (recipes) to do some common things
using brandseyer2. You should, for the most part, be able to copy and paste
them in to an R file, change a few variables (like the account code and filter),
and then run them.

# Recipes

## Finding topics for mentions

Sometimes you may want to get a clean data set of mentions, and the topics on them.
This small script will write out a CSV giving, for each topic on a mention, a row with the mention
ID, topic ID, and topic name. It reads all the mentions matching a filter, asking
for only the mentions' IDs and tags. Then, using `topics()`, it gets all the topic
data for the mentions. Next, it uses `dplyr::select()` to choose only some interesting
columns to keep. Finaly, it saves the data, using `readr::write_csv()`.

### The Recipe

```{r}
library(brandseyer2)
library(dplyr, warn.conflicts = FALSE)            # For manipulating tables
library(readr)                                    # For writing CSVs

code <- "BEUB03AA"
filter <- "published inthelast week and brand isorchildof 46334"

mentions_with_topics <- account(code) %>%         # Get the account
  mentions(filter, select = c(id, tags)) %>%      # Ask for the mentions (but only their IDs and tags)
  topics() %>%                                    # From the mentions, get specific topics
  select(id, topic.id, name)                      # Select only some interesting columns


write_csv(mentions_with_topics, "topics.csv")

```

### Outcomes

You can modify what columns you'd like kept in your CSV file by modifying the `select` line. 
And this is what some of the data looks like:

```{r echo=FALSE}
mentions_with_topics
```

