---
title: "The brandseyer2 Cookbook"
author: "Constance Neeser"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The brandseyer2 Cookbook}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This is a collection of short scripts (recipes) to do some common things
using brandseyer2. You should, for the most part, be able to copy and paste
them in to an R file, change a few variables (like the account code and filter),
and then run them.

# Recipes

## Finding topics for mentions

Sometimes you may want to get a clean data set of mentions, and the topics on them.
This small script will write out a CSV giving, for each topic on a mention, a row with the mention
ID, topic ID, and topic name. It reads all the mentions matching a filter, asking
for only the mentions' IDs and tags. Then, using `topics()`, it gets all the topic
data for the mentions. Next, it uses `dplyr::select()` to choose only some interesting
columns to keep. Finaly, it saves the data, using `readr::write_csv()`.

### The Recipe

```{r, eval=FALSE}
library(brandseyer2)
library(dplyr, warn.conflicts = FALSE)            # For manipulating tables
library(readr)                                    # For writing CSVs

code <- "BEUB03AA"
filter <- "published inthelast week and brand isorchildof 46334"

mentions_with_topics <- account(code) %>%         # Get the account
  mentions(filter, select = c(id, tags)) %>%      # Ask for the mentions (but only their IDs and tags)
  topics() %>%                                    # From the mentions, get specific topics
  select(id, topic.id, name)                      # Select only some interesting columns


write_csv(mentions_with_topics, "topics.csv")

```

### Outcomes

You can modify what columns you'd like kept in your CSV file by modifying the `select` line. 
And this is what some of the data looks like:

```{r}
#> # A tibble: 2,475 x 3
#>    id          topic.id name                                              
#>    <chr>          <int> <chr>                                             
#>  1 46334-8933…    70331 Comparing (brands to brands) or comparing (brands…
#>  2 46334-8933…    69873 Ethics or reputation                              
#>  3 46334-8933…    71303 Transport experience                              
#>  4 46334-8933…    71359 Drivers                                           
#>  5 46334-8933…    69878 Accusations of unethical behavior                 
#>  6 46334-8933…    69873 Ethics or reputation                              
#>  7 46334-8933…    70331 Comparing (brands to brands) or comparing (brands…
#>  8 46334-8933…    69873 Ethics or reputation                              
#>  9 46334-8933…    70331 Comparing (brands to brands) or comparing (brands…
#> 10 46334-8933…    69873 Ethics or reputation                              
#> # ... with 2,465 more rows
```

## Average number of topics per mention

This is an extension of the recipe for finding topics on a mention. It uses 
dplyr to calculate the average number of mentions on a topic. 

### The Recipe

```{r, eval=FALSE}
library(brandseyer2)
library(dplyr)
library(readr)

code <- "BEUB03AA"
filter <- "published inthelast week and brand isorchildof 46334"

mentions_with_topics <- account(code) %>%         # Get the account
  mentions(filter, select = c(id, tags)) %>%      # Ask for the mentions (but only their IDs and tags)
  topics() %>%                                    # From the mentions, get specific topics
  select(id, topic.id, name)

topics_per_mention <- mentions_with_topics %>%   
  group_by(id) %>%                # For each mention
  summarise(count = n())          # Count the number of mentions

average_topics <- sum(topics_per_mention$count) / nrow(topics_per_mention)
message(glue::glue("The average number of topics per mention is {round(average_topics, 2)}"))
```

### The outcome

The recipe prints out the average

```{r}
#> The average number of topics per mention is 2.84
```

## Find the parent of topics

BrandsEye topics can belong to more than one topic tree, and so can have more
than one parent. When wanting to find the parent of a topic, you need to choose
a topic tree to do this from. The easiest way to find topic trees is to use the
`topic_trees()` function, like so:

```{r message=FALSE, warning=FALSE}
library(brandseyer2)
library(dplyr)

account("TEST01AA") %>% 
  topic_trees() %>% 
  select(id, name)
```

### The Recipe

```{r, eval=FALSE}
library(brandseyer2)
library(dplyr)

account("TEST01AA") %>% 
  tags() %>% 
  with_tag_parents(1001) %>% 
  filter(namespace == 'topic') %>% 
  arrange(desc(is_parent), name)

```

### The outcome

This produces a nicely sorted table of topics and parents, all in relation
to the given topic tree. Notice that the topic tree itself won't be in this
table, since it is in its own *topic_tree* namespace.

```{r, echo=FALSE}
library(brandseyer2)
library(dplyr)

account("TEST01AA") %>% 
  tags() %>% 
  with_tag_parents(1001) %>% 
  filter(namespace == 'topic') %>% 
  arrange(desc(is_parent), name) %>% 
  select(id, name, parent)

```

