---
title: "Filtering"
author: "Constance Neeser"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Filtering}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

- We probably need a vignette describing what a mention looks like. Although grouse 
  documentation?

# Introduction

This is an introduction

This will provide an introduction to filtering for data in BrandsEye

BrandsEye's API supports a small language to help you select exactly the mentions
that you want to select. You'll do this with the help of the `mentions()` function,
which always expects a filter. You can also count and aggregate mention data using
`count_mentions()`. We also have a query language, that this will introduce a bit of.

Combined with [dplyr][dplyr][^1] for manipulating data, [ggplot2][ggplot2][^2] for visualising data, 
and [readr][readr][^3]
for exporting data, brandseyer2 is a powerful tool for examining social media data. 

```{r}
library(brandseyer2)

account("TEST01AA") %>% 
  mentions(filter = "published inthelast week")  
```

# Filtering

## Dates

Dates first, since this allows people to constrain data, rather than get everything.
How do they cancel if they're accidently pulling more than they want to? 

- Published date is the important one
- How to filter on hours. 
- Addendum: picked up date, updated date, what are these.

### Grouping by date

- hour
- day
- week
- month 
- year


## Selecting mentions

- By ID
- by conversation ID

## Relevancy

> Relevancy isnt irrelevant 

## Sentiment 

## Tags

We introduce tags early, since topics are just tags.

## Topics

## Data verification

> process is verified

> crowdVerified is true

What's the difference, and when to use which. 

## Location

- Filtering by continents and large geographic regions.
- Filtering by country
- Filtering by country region / province / state.
- Filtering by city

Analyse is required to get all of these names.

## Language

## Gender

## Author information

## Finding replies and reshares


[^1]: [dplyr][dplyr] is an amazing library for manipulating data. After downloading
data using brandseyer2, it allows you to reshape the data to fit your needs.

[^2]: [ggplot2][ggplot2] is a rich visualisation library for R. After pulling data
from brandseyer2, ggplot2 is a great tool for visualising the data.

[^3]: [readr][readr] is a library for reading and writing CSV data. R has a rich ecosystem
for importing and exporting data, with other libraries providing support for Excel and Google Sheets.


[dplyr]: https://dplyr.tidyverse.org/
[ggplot2]: https://ggplot2.tidyverse.org/
[readr]: https://readr.tidyverse.org/
