---
title: "Filtering"
author: "Constance Neeser"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Filtering}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

- We probably need a vignette describing what a mention looks like. Although grouse 
  documentation?

# Introduction

This is an introduction

This will provide an introduction to filtering for data in BrandsEye

BrandsEye's API supports a small language to help you select exactly the mentions
that you want to select. You'll do this with the help of the `mentions()` function,
which always expects a filter. You can also count and aggregate mention data using
`count_mentions()`. We also have a query language, that this will introduce a bit of.

Combined with [dplyr][dplyr][^1] for manipulating data, [ggplot2][ggplot2][^2] for visualising data, 
and [readr][readr][^3]
for exporting data, brandseyer2 is a powerful tool for examining social media data. 

```{r}
library(brandseyer2)

account("TEST01AA") %>% 
  mentions(filter = "published inthelast week")  
```

# Filtering

## Dates

All mentions are published at a particular date and time. This is the most important
thing that you can filter on: the publication date. Most questions that we want to answer
usually have a constrained time period. For example,

> what was the sentiment towards our brand _last month_?

or

> how did sentiment change towards our brand over Christmas last year compared to Christmas
the year before?

The `published` field allows us to filter on mentions by their date of publication. For example,

> published after '2018/01/01'

will filter for mentions that are published _on or after_ the 1st of January, 2018. Note
that mentions published on the first are also included by the filter.

> published before '2018/02/01'

filters for mentions published strictly before the 1st of February, 2018. It _does not_
include mentions from the 1st of February. 

These two filters can be combined using the word `and`, like so:

> published after '2018/01/01' and published before '2018/02/01'

Some things to notice in this filter: it's made up of two _sub-filters_, the 
_after_ bit, and the _before_ bit. These have been combined using an `and`. Dates
themselves are quoted in single-quotes, like so: '2018/01/01'. 

Only mentions for which are published both after 2018/01/01 _and_ before 2018/02/02,
will be selected by this filter. In other words, this filter selects mentions published
during the month of January. 

We will have more to say about the connector `and` in a later section of this guide.

You can test this out now, using either analyse or brandseyer2.


### Trying this out

#### In analyse

The brand selector.

#### Using brandseyer2

All of our examples, going forward, will assume that you have access to 
your accounts, and that you're using brandseyer2. We won't do anything fancy,
just the bare minimum brandseyer2 to demonstrate the data.

```{r, eval = FALSE}
mentions <- account("QUIR01BA") %>% 
  filter_mentions("published after '2018/01/01' and published before '2018/02/01'" ) %>% 
  count_mentions
  
mentions
#> # A tibble: 1 x 1
#>   mentionCount
#>          <int>
#> 1        36592
```

So, we have 36 592 mentions published in the month of January. Instead of counting
the mentions with `count_mentions()`, you could instead use `mentions()`
to pull a table of all of these mentions.

### Relative dates

The filter language provides some convenient shortcuts. A common one is
to find mentions from the last week

> published inthelast week

Notice that `inthelast` is written as one word. 

Similarly, we can find mentions

- published inthelast hour
- published inthelast 24hours
- published inthelast day
- published inthelast week
- published inthelast month 
- published inthelast quarter
- published inthelast year







Dates first, since this allows people to constrain data, rather than get everything.
How do they cancel if they're accidently pulling more than they want to? 

- Published date is the important one
- How to filter on hours. 
- Addendum: picked up date, updated date, what are these.

### Grouping by date

- hour
- day
- week
- month 
- year


## Selecting mentions

- By ID
- by conversation ID

## Relevancy

> Relevancy isnt irrelevant

## Joining together statements

- What is `AND`? Both things must be true.
- What is `OR`? Either things must be true.  
- It's not English! There's a distinct meaning.
- This is called _Boolean Logic_, or _Boolean Algebra_[^4], after George Boole, a 
  mathematician who published in the 1800s on logic and "rules of thought".

## Sentiment 

## Tags

We introduce tags early, since topics are just tags.

## Topics

## Data verification

> process is verified

> crowdVerified is true

What's the difference, and when to use which. 

## Things that should always be in filters

- brands
- topic trees?

## Location

- Filtering by continents and large geographic regions.
- Filtering by country
- Filtering by country region / province / state.
- Filtering by city

Analyse is required to get all of these names.

## Language

## Gender

## Joining together statements revisted

Now that we have more statements, we can give more examples. 

- Precedence.
- Bracketing.

## Author information

## Finding replies and reshares


[^1]: [dplyr][dplyr] is an amazing library for manipulating data. After downloading
data using brandseyer2, it allows you to reshape the data to fit your needs.

[^2]: [ggplot2][ggplot2] is a rich visualisation library for R. After pulling data
from brandseyer2, ggplot2 is a great tool for visualising the data.

[^3]: [readr][readr] is a library for reading and writing CSV data. R has a rich ecosystem
for importing and exporting data, with other libraries providing support for Excel and Google Sheets.

[^4]: You can ead more about Boolean Logic on [Wikipedia](https://en.wikipedia.org/wiki/Boolean_algebra).

[dplyr]: https://dplyr.tidyverse.org/
[ggplot2]: https://ggplot2.tidyverse.org/
[readr]: https://readr.tidyverse.org/
